---
title: "Exercise 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
list.of.packages <- c("learnr","shiny","remotes")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(learnr)
require(remotes)
if(!("gradethis" %in% installed.packages())){remotes::install_github("rstudio/gradethis")}
require(gradethis)

gradethis::gradethis_setup()
```

## Introduction

This is the first of the weekly exercises. These exercises are designed to reinforce content taught in the first demonstration. Typically, they consist of quiz questions and/or R exercises that require you to enter code into a box. These exercises are split into beginner and advance sections. It is expected that students can complete the beginner sections of each weekly exercise, with the advanced sections designed for students who want an extra challenge or learn additional functions in R. If you are struggling, each exercise comes with a number of hints that may be helpful.

## Basic Exercises

### Question 1

```{r question_1,echo = FALSE}
quiz(
  question("If you're struggling with R and coding, where can you find help? Select all correct answers.",
    answer("Google.",correct = TRUE),
    answer("Using the help() function.",correct = TRUE),
    answer("Ask your fellow classmates.",correct = TRUE),
    answer("Ask your lecturer (contactable after class, via email, or via the discussion boards on Canvas).",correct = TRUE),allow_retry = TRUE
  )
)
```

### Question 2

The following code calculates two plus two and saves the object as `x`. Edit the code so that the code calculates two plus five and save the result as object `x`:

```{r question_2, exercise=TRUE,exercise.lines = 5}
x <- 2 + 2

x
```

```{r question_2-hint-1}
Remember, R is like a calculator.
```

```{r question_2-hint-2}
Use `<-` to save objects.

Next hint will show the solution...
```

```{r question_2-solution}
x <- 2 + 5

x
```

```{r question_2-code-check}
grade_code()
```

### Question 3

The following code calculates two plus two and saves the object as `x`. Add to this by writing additional code that calculates three plus three and saves the result as `y`, then multiply `x` and `y` and save the result as `z`:

```{r question_3, exercise=TRUE,exercise.lines = 5}
x <- 2 + 2
```

```{r question_3-hint-1}
You can put new commands on separate lines.
```

```{r question_3-hint-2}
Use the `*` symbol to multiply two numbers.

Next hint will show the solution...
```

```{r question_3-solution}
x <- 2 + 2
y <- 3 + 3
z <- x * y
```

```{r question_3-code-check}
grade_code()
```

### Question 4

The following code save 3.14 as the object `x`. Use the `floor()` function to round this number down to the nearest whole number and save the result as `y`.

```{r question_4, exercise=TRUE,exercise.lines = 5}
x <- 3.14

```

```{r question_4-hint-1}
Using a function follows this template: function_name(argument)
```

```{r question_4-hint-2}
You may want to google how to use the `floor()` function.

Next hint will show the solution...
```

```{r question_4-solution}
x <- 3.14
y <- floor(x)
```

```{r question_4-code-check}
grade_code()
```

### Question 5

The following code saves a number with many decimal places as the object `x`. Use a function that rounds `x` to four decimal places and save the result as `y`.

```{r question_5, exercise=TRUE,exercise.lines = 5}
x <- 3.14159265359

```

```{r question_5-hint-1}
Try googling to find a function that rounds numbers to decimal places.
```

```{r question_5-hint-2}
Some functions take more than one argument...

Next hint will show the solution...
```

```{r question_5-solution}
x <- 3.14159265359
y <- round(x,digits = 4)
```

```{r question_5-code-check}
grade_code()
```

### Question 6

My three favourite numbers are 53, 8, and 21, and my three favourite colours are maroon, blue, and gold. Edit the following code to save a numeric vector with my three favourite numbers to `my_fav_numbers`. Also, save a character vector with my three favourite colours to `my_fav_colours`.

```{r question_6, exercise=TRUE,exercise.lines = 5}
my_fav_numbers <- c()
my_fav_colours <- c()

```

```{r question_6-hint-1}
A vector is a list of ordered elements. You can create a vector using the function: `c(element1,element2,etc.)`, where each element is separated by a comma.
```

```{r question_6-hint-2}
To create a character, put the words in quotation marks (e.g., "This is now a character.")

Next hint will show the solution...
```

```{r question_6-solution}
my_fav_numbers <- c(53,8,21)
my_fav_colours <- c("maroon","blue","gold")
```

```{r question_6-code-check}
grade_code()
```

### Question 7

Below, an object is saved as `mystery.object`. Answer the quiz question below about this object.

```{r question_7-setup, include = FALSE}
mystery.object <- factor(c("what class does this object have?","it is a mystery!","super spooky..."),levels = c("what class does this object have?","it is a mystery!","super spooky..."))
```

```{r question_7, exercise=TRUE,exercise.lines = 5}
#mystery.object

```

```{r question_7-hint-1}
Calling the object in the console (running to code) may give you some insight...
```

```{r question_7-hint-2}
Is there a function that allows you to determine the class of an object?

Next hint will show the solution...
```

```{r question_7-solution}
class(mystery.object)
```

```{r question_7-quiz,echo = FALSE}
quiz(
  question("What class does `mystery.object` have?",
    answer("Numeric"),
    answer("Character"),
    answer("Factor",correct = TRUE),
    answer("Logical"),allow_retry = TRUE
  )
)
```

### Question 8

First, write code that saves a numeric vector with my three favourite numbers (53,8,21) to `my_fav_numbers`. Then, use vector operations to multiply my three favourite numbers by 3 and save the result as `fav_numbers_times_3`.

```{r question_8, exercise=TRUE,exercise.lines = 5}


```

```{r question_8-hint-1}
`fav_numbers_times_3` should be a numeric vector with a length of three.
```

```{r question_8-hint-2}
You can use vector operations to multiply your three favourite numbers at once.

Next hint will show the solution...
```

```{r question_8-solution}
my_fav_numbers <- c(53,8,21)
fav_numbers_times_3 <- my_fav_numbers * 3
```

```{r question_8-code-check}
grade_code()
```

### Question 9

Below, the object `numbers` is saved, which is a numeric vector. Use a function to get the absolute values of `numbers` and save the result as `abs_numbers`. (The absolute value of a number is the size of the number, regardless of whether it is positive or negative; for example, the absolute value of `-5` is `5`))

```{r question_9-setup, include = FALSE}
numbers <- c(1,-2,6,-53,-88,100,3.14,-13)
```

```{r question_9, exercise=TRUE,exercise.lines = 5}
#numbers

```

```{r question_9-hint-1}
You may need to google what R function calculates the absolute value of a vector...
```

```{r question_9-hint-2}
Some functions take a vector as an argument. For example, `sqrt()` can take a numeric vector to calculate the square root of many numbers at once.

Next hint will show the solution...
```

```{r question_9-solution}
abs_numbers <- abs(numbers)
```

```{r question_9-code-check}
grade_code()
```

### Question 10

Here are some quiz questions about data tables (or data.frames in R).

```{r question_10-quiz, echo = FALSE}
quiz(
  question("Typically, each column in a data table represents:",
    answer("A variable.", correct = TRUE),
    answer("Data from a single participant."),
    answer("The number of participants."),
    answer("A numeric value."),allow_retry = TRUE,random_answer_order = TRUE
  )
)
```

```{r question_11-quiz,echo = FALSE}
quiz(
  question("Typically, each row in a data table represents:",
    answer("A variable."),
    answer("Data from a single participant.", correct = TRUE),
    answer("The number of participants."),
    answer("A numeric value."),allow_retry = TRUE,random_answer_order = TRUE
  )
)
```

Congrats! This is end of the basic exercises for this week. If you looking for an extra challenge, or wish to practice your R skills a bit more, why not try the advanced exercises?

## Advanced Exercises

This week's advanced exercises focuses on introducing two other object classes (lists and matrices) and syntax for selecting specific elements in vectors and data.frames (known as indexing). This knowledge is particularly helpful for advanced procedures (e.g., creating your own functions), but can also provide helpful shortcuts for every day coding.

NOTE: Content in these advanced exercises are NOT covered in demonstrations. The purpose is to provide additional challenges or new R content for students looking for a challenge. Also, there is no code checking for advanced exercises - you are required to evaluate whether the code meets the objective on your own. However, if you want an example of a possible answer, you can click through the hints.

### Question 1A - Lists in R

Lists are the most flexible objects in R. Similar to vectors, lists are an ordered set of elements; however, unlike vectors, the elements within a list can contain different classes of objects. For example, the first element of a list could be a single numeric vector, the second could be a character vector, the third could be an entire data.frame, and fourth could be another list! Lists are most useful for advanced coding or creating your own R functions. For all content covered in this module, using vectors will be sufficient.

To create a list, use the `list()` function, where each argument is a separate element in the list.
```{r,eval = FALSE,echo = TRUE}
list(element1,element2,etc)
```

In the code box below, create a list where the first element is a vector with your three favourite numbers, the second element is a vector with your three favourite colours, and the third is a logical value answering this question: "Do you love coding in R?" Save the list as an object called 'responses'.

```{r question_a1, exercise=TRUE,exercise.lines = 5}


```

```{r question_a1-hint-1}
Remember, to create a vector, use the `c()` function.
```

```{r question_a1-hint-2}
To complete the task, you will need to fill in the following code:
  
list(c(),c(),TRUE)

Next hint will show the solution...
```

```{r question_a1-solution}
responses <- list(c(53,8,42),c("blue","maroon","gold"),TRUE)

#Note: your favourite numbers and colours could be different from mine. Whether or not you love coding should always be TRUE.
```

### Question 2A - Selecting Elements in a List

Elements of a list can be accessed individually by using indexing. In a list, this involves using double square brackets `[[...]]` that contains the number of the element you wish to select.

So, if you wish to select the third element of a list called `this_list`, you would run the following code. You could then run any operation or function on this object as if it were any ordinary object.

```{r,eval = FALSE,echo = TRUE}
this_list[[3]]
```

In the code box below, there is an object called `elements5`. Using indexing, select the 5th element of this list. If it is a numeric object, multiply it by 3 and save the result as `the_5th_element`. If it is a character object, simply save the object as `the_5th_element`.

```{r question_a2-setup, include = FALSE}
elements5 <- list("earth","fire","wind","water","heart")
```

```{r question_a2, exercise=TRUE,exercise.lines = 5}
#elements5

the_5th_element <-

```

```{r question_a2-hint-1}
You can use the following functions to determine if an object is a numeric or a character object:
  
is.numeric()
is.character()

You could also use the class() function.
```

```{r question_a2-hint-2}
To determine if the 5th element of a list is a numeric object, you could use the following code:
  
is.numeric(element5[[5]])

Next hint will show the solution...
```

```{r question_a2-solution}
is.numeric(element5[[5]])
is.character(element5[[5]])
#Note: this code determines that the 5th element is a character.

the_5th_element <- element5[[5]]
```

### Question A3 - Selecting Elements from a Vector

Similar to how elements of a list can be accessed individually by using indexing, indexing can also be used to select individual elements of a vector. The difference between indexing for lists and vectors, however, is that vectors only use single square brackets.

So, if you wish to select the third element of a vector called `this_vector`, you would run the following code.

```{r,eval = FALSE,echo = TRUE}
this_vector[3]
```

To select a range of elements, you can use a colon. For instance, the code below selects all elements between the third and the ninth element.

```{r,eval = FALSE,echo = TRUE}
this_vector[3:9]
```

You can even use a numeric vector within the indexing. The code below selects only the first, third, and fifth elements:

```{r,eval = FALSE,echo = TRUE}
this_vector[c(1,3,5)]
```

In the code box below, there is an object called `numeric_vector`, which is a vector of numbers. Using indexing, multiply the 53rd and 88th element of the vector. Save the result as an object called `product`.

```{r question_a3-setup, include = FALSE}
numeric_vector <- 1:100 * 7
```

```{r question_a3, exercise=TRUE,exercise.lines = 5}
#numeric_vector

product <- 

```

```{r question_a3-hint-1}
The following code will tell you the 4th element of the vector...
  
numeric_vector[4]
```

```{r question_a3-hint-2}
A vector element that has been indexed can have operations performed on it as normal...

Next hint will show the solution...
```

```{r question_a3-solution}
product <- numeric_vector[53] * numeric_vector[88]
```

### Question A4 - Matrices in R

Matrices are R objects in which the elements are arranged in a two-dimensional rectangular layout, similar to a data.frame. However, unlike a data.frame, all elements within a matrix is of the same class. Matrices are helpful when you need to store multi-dimensional data, but we tend not to use them in psychological research. In almost all cases, a data.frame will suit our needs better.

You can create a matrix from scratch using the `matrix()` function. The first argument is a vector input which will become the elements of the matrix. You will also need to specify the number of rows, and columns, and whether you want the input to be read in by row or by column.

The following code makes a 2 x 3 matrix that is read in by row.
```{r,echo = TRUE}
the_matrix <- matrix(c(1,2,3,4,5,6),nrow = 2,ncol = 3,byrow = TRUE)
```

You can also convert data.frames to matrices and vice versa using the following functions.

```{r,echo = TRUE}
the_matrix <- matrix(c(1,2,3,4,5,6),nrow = 2,ncol =2,byrow = TRUE)

#Convert to data.frame
matrix_reloaded <- as.data.frame(the_matrix)

#Convert back to matrix
matrix_revolutions <- as.matrix(matrix_reloaded)
```

Below, ratings of anxiety were recorded from a single participant 4 times a day for 7 days. These ratings were recorded in chronological order in a numeric vector. Convert this vector into a matrix, so that each column represents a day, while each row represents the 4 times a day. Then convert the matrix to a data.frame. Save the final data.frame as `anxiety.data`.

```{r question_a4-setup, include = FALSE}
anxiety_ratings <- c(4,3,6,4,2,3,4,3,6,5,6,4,2,3,1,2,4,4,3,3,7,6,7,7,6,6,5,5)
```

```{r question_a4, exercise=TRUE,exercise.lines = 5}
#anxiety_ratings

anxiety.matrix <-

anxiety.data <-

```

```{r question_a4-hint-1}
Use the `matrix()` function to create a matrix from a vector.
Set the number of rows to the number of days.
```

```{r question_a4-hint-2}
Since ratings were collected in chronological order, you will need to tell the `matrix()` function to read the input by column...

Next hint will show the solution...
```

```{r question_a4-solution}
anxiety_ratings

anxiety.matrix <- matrix(anxiety_ratings,nrow = 4,ncol = 7,byrow = FALSE)

anxiety.data <- as.data.frame(anxiety.matrix)
```

### Question A5 - Indexing Matrices and Data.frames

Similar to lists and vectors, individual elements of matrices and data.frames can be accessed via indexing. Indexing is the same for both matrices and data.frames. To select an individual element, use the square brackets after the name of the matrix/data.frame followed by the row number, then a comma, then the column number.

So to select the element in the 2nd row and the 3rd column from the following data.frame, you would use the following code:
```{r,eval = FALSE,echo = TRUE}
this.data[2,3]
```

In the anxiety data above, you wish to add the anxiety ratings from the afteroon and evening (rows 3 and 4) for the weekends only (columns 6 and 7). Use indexing to achieve this and save the final result as `total.anxiety`.

```{r question_a5-setup, include = FALSE}
anxiety_ratings <- c(4,3,6,4,2,3,4,3,6,5,6,4,2,3,1,2,4,4,3,3,7,6,7,7,6,6,5,5)

anxiety.matrix <- matrix(anxiety_ratings,nrow = 4,ncol = 7,byrow = FALSE)

anxiety.data <- as.data.frame(anxiety.matrix)
colnames(anxiety.data) <- c("Mon","Tue","Wed","Thur","Fri","Sat","Sun")
```

```{r question_a5, exercise=TRUE,exercise.lines = 5}
#anxiety.data

total.anxiety
```

```{r question_a5-hint-1}
Once you have index a single element, you can perform operations (such as addition) like it is an ordinary object.
```

```{r question_a5-hint-2}
To add the afternoon and evening ratings for Sunday, you could use the following code:

anxiety.data[3,7] + anxiety.data[4,7]

Next hint will show the solution...
```

```{r question_a5-solution}
anxiety.data[3,6] + anxiety.data[4,6] + anxiety.data[3,7] + anxiety.data[4,7]
```

### Question A6 - Indexing Columns from Data.frames

Rather than indexing a single element from a data.frame, you can also index an entire column. This is a handy shortcut to select all responses on a variable in a data.frame. This is done by calling the data.frame and variable you want to select, and separating them using the '$' symbol.

For example, if you wanted to select the variable `var2` in the data.frame called `this.data`, you could use the following code:
```{r,eval = FALSE,echo = TRUE}
this.data$var2
```

In the anxiety data above, you wish to determine which time (morning, midday, afternoon, or evening; rows 1 through 4 respectively) during the weekdays (Mon through Fri) were given the highest total anxiety ratings. Use indexing to achieve this.

```{r question_a6-setup, include = FALSE}
anxiety_ratings <- c(4,3,6,4,2,3,4,3,6,5,6,4,2,3,1,2,4,4,3,3,7,6,7,7,6,6,5,5)

anxiety.matrix <- matrix(anxiety_ratings,nrow = 4,ncol = 7,byrow = FALSE)

anxiety.data <- as.data.frame(anxiety.matrix)
colnames(anxiety.data) <- c("Mon","Tue","Wed","Thur","Fri","Sat","Sun")
```

```{r question_a6, exercise=TRUE,exercise.lines = 5}
#anxiety.data

total.anxiety
```

```{r question_a6-hint-1}
If two vectors of equal length are added together, the additions are done element-wise
(ie. element 1 is added to element 1, element 2 is added to element 2, etc.).
```

```{r question_a6-hint-2}
You could add each element together and see which time received the highest total rating.

Next hint will show the solution...
```

```{r question_a6-solution}
anxiety.data$Mon + anxiety.data$Tue + anxiety.data$Wed + anxiety.data$Thur + anxiety.data$Fri
```

```{r question_a6-quiz}
quiz(
  question("Which timeslot received the highest total rating?",
    answer("Morning"),
    answer("Midday"),
    answer("Afternoon",correct = TRUE),
    answer("Evening"),allow_retry = TRUE,random_answer_order = TRUE
  )
)
```