---
title: "1intro_workbook"
output: html_document
---

#Beginner

## Question 1.
In the chunk below, create an object called `numbers` which is a numeric vector containing your three favourite numbers.

```{r w1q1}
numbers <- NULL
```

## Question 2

Using vectorised operation, create an object called `numbers3` that multiplies the object `numbers` by 3.

The chunk below creates an integer vector `ages` with the ages of five people. (Note: defining a number with the sufficx `L`, e.g., `26L`, defines `26` as type integer rather than type double.)  Calculate how old they will be in ten years using a vectorized operation and store the result in the variable `ages_10`.

```{r Q2}
numbers3 <- NULL
```

## Question 3

Make a function that adds the elements of numbers3 together called `numbers_add`.

```{r}
numbers_add <- NULL
```

## Question 4

The code below has an error. Find and fix the error.
```{r}

```

## Question 5

Google... Class?

```{r}

```

#Intermediate

## Question 6

```{r}

```
#Advance

Create a data.frame called `data` with the following variables. Realistic values (e.g., age cannot be 1000 years).

age
marriage


For continuous variables, class as numeric.
For ordinal variables, class as...
For categorical variables, class as character or factor.

```{r}

```