---
title: "Exercise 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE,message = FALSE}
list.of.packages <- c("learnr","shiny","tidyverse","dplyr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(learnr)
require(tidyverse)
require(dplyr)
knitr::opts_chunk$set(echo = FALSE)

checker <- function(label,user_code,solution_code,check_code,envir_result,evaluate_result,envir_prep,...){
  
  envir_result
  out <- list(message = sample(c("Good Job!",
                                 "Well done!",
                                 "Great stuff!",
                                 "That is correct!",
                                 "Correct! You are really good at this."),1), correct = TRUE, location = "append")
  
#Question 1
if(label == "question_1"){
    if(!exists("x")){
    	out <- list(message = "No object saved as x. If there is a typo in the code, R will give you an error message and the line will not run.", correct = FALSE, location = "append")
    } else {
		if(!is.numeric(x)){
			out <- list(message = "x is not a numeric vector.", correct = FALSE, location = "append")
		}
	}
}

#Question 2
if(label == "question_2"){
    if(!exists("x")){
    	out <- list(message = "No object saved as x. If there is a typo in the code, R will give you an error message and the line will not run.", correct = FALSE, location = "append")
    } else {
		if(!is.character(x)){
			out <- list(message = "x is not a character vector.", correct = FALSE, location = "append")
		}
	}
}  

#Question 4
if(label == "question_4"){
    if(!exists("numbers")){
    	out <- list(message = "No object saved as numbers. Do not alter the numeric vector saved as numbers.", correct = FALSE, location = "append")
    } else {
		if(!identical(numbers,c(4,1,29,0,53,31))){
			out <- list(message = "The numeric vector saved as numbers does not match the original input. Do not edit the line that saves the object `numbers`. Click the `Start Over` button if necessary.", correct = FALSE, location = "append")
		} else {
			if(!exists("mean_of_numbers")){
				out <- list(message = "No object saved as `mean_of_numbers` was found.", correct = FALSE, location = "append")
			} else {
				if(mean_of_numbers != mean(numbers)){
					out <- list(message = "The number saved as `mean_of_numbers` does not match the correct mean.", correct = FALSE, location = "append")
				}
			}
		}
	}
}

if(label == "question_5"){
    if(!exists("numbers")){
    	out <- list(message = "No object saved as numbers. Do not alter the numeric vector saved as numbers.", correct = FALSE, location = "append")
    } else {
		if(!identical(numbers,c(1,2,2,3,3,3,4,4,4,4,5,5,5,6,6,7,NA,NA,NA))){
			out <- list(message = "The numeric vector saved as numbers does not match the original input. Do not edit the line that saves the object `numbers`. Click the `Start Over` button if necessary.", correct = FALSE, location = "append")
		} else {
			if(!exists("sd_of_numbers")){
				out <- list(message = "No object saved as `sd_of_numbers` was found.", correct = FALSE, location = "append")
			} else {
				if(is.na(sd_of_numbers)){
					out <- list(message = "The number saved as `sd_of_numbers` is missing. Certain functions don't deal well with missing data. Have you accounted for this?", correct = FALSE, location = "append")
				} else {
					if(sd_of_numbers != sd(numbers,na.rm = TRUE)){
						out <- list(message = "The number saved as `sd_of_numbers` does not match the correct standard deviation.", correct = FALSE, location = "append")
					}
				}
			}
		}
	}
}  

#Question 6
if(label == "question_6"){
    if(!exists("numbers")){
    	out <- list(message = "No object saved as numbers. Do not alter the numeric vector saved as numbers.", correct = FALSE, location = "append")
    } else {
		if(!identical(numbers,c(34958,293487,123874,98475,47389,3847,4897,75639))){
			out <- list(message = "The numeric vector saved as numbers does not match the original input. Do not edit the line that saves the object `numbers`. Click the `Start Over` button if necessary.", correct = FALSE, location = "append")
		} else {
			if(!exists("range_of_numbers")){
				out <- list(message = "No object saved as `range_of_numbers` was found.", correct = FALSE, location = "append")
			} else {
				if(range_of_numbers != max(numbers,na.rm = TRUE) - min(numbers,na.rm = TRUE)){
						out <- list(message = "The number saved as `range_of_numbers` does not match the correct range.", correct = FALSE, location = "append")
				}
			}
		}
	}
}

#Question 7
if(label == "question_7"){
    if(!exists("data")){
    	out <- list(message = "No object saved as data. Do not alter the data.frame as data.", correct = FALSE, location = "append")
    } else {
		  correct_data <- data.frame(ID = c(1,2,3,4,5,6,7,8,9,10),
                   var1 = c(10,29,38,47,56,13,24,35,46,57),
                   var2 = c(10.5,11,2,9,4,6,8,5.3,2.9,10))
      if(!identical(data,correct_data)){
			out <- list(message = "The data.frame saved as data does not match the original input. Do not edit the object saved as `data`. Click the `Start Over` button if necessary.", correct = FALSE, location = "append")
		} else {
			if(!exists("descript_stats")){
				out <- list(message = "No object saved as `descript_stats` was found.", correct = FALSE, location = "append")
			} else {
				
				correct_answer <- summarise(data,	mean_var1 = mean(var1),
											sd_var1 = sd(var1),
											mean_var2 = mean(var2),
											sd_var2 = sd(var2))
				
				if(!identical(descript_stats,correct_answer)){
						out <- list(message = "The data.frame saved as `correct_answer` does not match the correct answer.", correct = FALSE, location = "append")
				}
			}
		}
	}
}

#Question 8
if(label == "question_8"){

	if(!exists("data")){
    	out <- list(message = "No object saved as data. Do not alter the data.frame as data.",
    				correct = FALSE,
    				location = "append")
    } else {
		correct_data <- data.frame(ID = c(1,2,3,4,5,6,7,8,9,10),
                   var1 = c(10,92,NA,74,65,31,42,53,64,75),
                   var2 = c(10.5,11,2,9,4,6,8,5.3,2.9,10))
		if(!identical(data,correct_data)){
			out <- list(message = "The data.frame saved as data does not match the original input. Do not edit the object saved as `data`. Click the `Start Over` button if necessary.", correct = FALSE, location = "append")
		} else {
			if(!exists("data_minmax")){
				out <- list(message = "No object saved as `data_minmax` was found.", correct = FALSE, location = "append")
			} else {
				correct_answer <- summarise(data,
                          max_var1 = max(var1,na.rm = TRUE),
                          min_var1 = min(var1,na.rm = TRUE),
                          max_var2 = max(var2,na.rm = TRUE),
                          min_var2 = min(var2,na.rm = TRUE)
                          )
				if(!identical(colnames(data_minmax),colnames(correct_answer))){
					out <- list(message = "The column names of `data_minmax` is not detected to be in the same order as specified above.", correct = FALSE, location = "append")
				} else {
					if(!identical(data_minmax,correct_answer)){
						out <- list(message = "The data.frame saved as `correct_answer` does not match the correct answer.", correct = FALSE, location = "append")
					}
				}
			}
		}
	}
}

#Question 9
if(label == "question_9"){
    if(!exists("missing_values")){
    	out <- list(message = "No object saved as `missing_values`.", correct = FALSE, location = "append")
    } else {
		if(is.character(missing_values)){
			out <- list(message = "Something is wrong with the code. Edit the code such that `is.na(missing values)` returns a correct response of three `FALSE` and three `TRUE`.", correct = FALSE, location = "append")
		} else {
			if(!identical(is.na(missing_values),c(FALSE,FALSE,FALSE,TRUE,TRUE,TRUE))){
				out <- list(message = "You seem to be on the correct track, but the code is not entirely correct. Edit the code such that `is.na(missing values)` returns a correct response of three `FALSE` and three `TRUE`.", correct = FALSE, location = "append")
			}
		}
	}
}
  
#Question 10
if(label == "question_10"){
    if(!exists("animals")){
    	out <- list(message = "No object saved as `animals`. Do not alter the character vector saved as animals.", correct = FALSE, location = "append")
    } else {
		if(!identical(animals,c("cat","magpie","lion","eagle","tiger",NA,"crow",NA,NA,"bulldog","hawk","kangaroo",NA,"swan",NA,NA,NA,NA))){
			out <- list(message = "The vector saved as animals does not match the original input. Do not edit the object saved as `animals`. Click the `Start Over` button if necessary.", correct = FALSE, location = "append")
		} else {
			if(!exists("NA_total")){
				out <- list(message = "No object saved as `NA_total` was found.", correct = FALSE, location = "append")
			} else {
				if(!identical(NA_total,sum(is.na(animals)))){
					out <- list(message = "The number saved as `NA_total` is incorrect.", correct = FALSE, location = "append")
				}
			}
		}
	}
}
        
return(out)
}

tutorial_options(exercise.checker = checker)
```

## Introduction

This is the second of the weekly exercises. These exercises are designed to reinforce content taught in the second demonstration. Typically, they consist of quiz questions and/or R exercises that require you to enter code into a box. These exercises are split into beginner and advance sections. It is expected that students can complete the beginner sections of each weekly exercise, with the advanced sections designed for students who want an extra challenge or learn additional functions in R. If you are struggling, each exercise comes with a number of hints that may be helpful.

## Basic Exercises

### Question 1

There is a typo in the following code that is preventing it from running successfully. Fix the typo to save a numeric vector to `x`.

```{r question_1, exercise=TRUE}
x <- c(1, 2, 3  4, 5)
```

```{r question_1-hint-1}
Very common typos include missing components that make the code run successfully.
```

```{r question_1-hint-2}
Elements in a function are separated by commas.

Next hint will show the solution...
```

```{r question_1-solution}
#The comma after the 3 is missing.
x <- c(1, 2, 3, 4, 5)
```

```{r question_1-check}
checker()
```

### Question 2

The following code is attempting to save a character vector as `x`. However, the code is not running successfully. Find the error and fix it.

```{r question_2, exercise=TRUE}
x <- c(Maroon, Blue, Gold)
```

```{r question_2-hint-1}
Very common typos include missing components that make the code run successfully.
```

```{r question_2-hint-2}
R differentiates character strings and object names from the use of quotation marks... 

Next hint will show the solution...
```

```{r question_2-solution}
#The character strings are missing quotation marks.
x <- c("Maroon", "Blue", "Gold")
```

```{r question_2-check}
checker()
```


### Question 3

```{r question_3-quiz}
quiz(
  question("What are the advantages of using a script to analyse data? Select all correct answers.",
    answer("Reduces human error.",correct = TRUE),
    answer("Keeps a record of manipulations on datasets.",correct = TRUE),
    answer("Is easily shareable and reproducible.",correct = TRUE),
    answer("A change can be introduced in the analysis pipeline without re-doing the whole process.", correct = TRUE),allow_retry = TRUE ,random_answer_order = TRUE
  )
)
```

### Question 4

Calculate the mean of the following numbers, and save the result as an object named `mean_of_numbers`.

```{r question_4, exercise=TRUE}
numbers <- c(4,1,29,0,53,31)

mean_of_numbers <- 
```

```{r question_4-hint-1}
Base R has a function that can compute the mean for you.
```

```{r question_4-hint-2}
The function `mean()` takes a numeric vector as the first argument.

Next hint will show the solution...
```

```{r question_4-solution}
numbers <- c(4,1,29,0,53,31)

mean_of_numbers <- mean(numbers)
```

```{r question_4-check}
checker()
```

### Question 5

Below is an object called `numbers` that is a numeric vector. Calculate the standard deviation of this vector and save the results as an object called `sd_of_numbers`.

```{r question_5-setup, include = FALSE}
numbers <- c(1,2,2,3,3,3,4,4,4,4,5,5,5,6,6,7,NA,NA,NA)
```

```{r question_5, exercise=TRUE,exercise.lines = 5}
numbers

```

```{r question_5-hint-1}
Base R has a function that calculates the standard deviation of a numeric vector.
```

```{r question_5-hint-2}
Is there any missing values in the numeric vector `numbers`?

Next hint will show the solution...
```

```{r question_5-solution}
#You are required to set `na.rm = TRUE` to ignore missing values.
sd_of_numbers <- sd(numbers,na.rm = TRUE)
```

```{r question_5-check}
checker()
```

### Question 6

Below is an object called `numbers` that is a numeric vector. Calculate the range of this vector and save the results as an object called `range_of_numbers`.

```{r question_6-setup, include = FALSE}
numbers <- c(34958,293487,123874,98475,47389,3847,4897,75639)
```

```{r question_6, exercise=TRUE,exercise.lines = 7}
numbers

```

```{r question_6-hint-1}
The range of a set of numbers is the largest number of the set minus the smallest number of the set.
```

```{r question_6-hint-2}
Once you have saved the results of a function to an object, you can perform operations on them like with any other object.

Next hint will show the solution...
```

```{r question_6-solution}
max_of_numbers <- max(numbers,na.rm = TRUE)
min_of_numbers <- min(numbers,na.rm = TRUE)

range_of_numbers <- max_of_numbers - min_of_numbers

#The above code can also be written in one line:
range_of_numbers <- max(numbers,na.rm = TRUE) - min(numbers,na.rm = TRUE)
```

```{r question_6-check}
checker()
```

### Question 7

Below is a data.frame called `data`. Edit the code below to use the summarise function to calculate the mean and standard deviation of `var1` and `var2`. Save the result as `descript_stats`. Do not adjust the new variable names in the summarise function.

```{r,echo = FALSE}
data <- data.frame(ID = c(1,2,3,4,5,6,7,8,9,10),
                   var1 = c(10,29,38,47,56,13,24,35,46,57),
                   var2 = c(10.5,11,2,9,4,6,8,5.3,2.9,10))
```
```{r}
data
```

```{r question_7-setup, include = FALSE}
#source("https://raw.githubusercontent.com/antlee53/stirpsychstats/master/exercises/dependencies.R")

data <- data.frame(ID = c(1,2,3,4,5,6,7,8,9,10),
                   var1 = c(10,29,38,47,56,13,24,35,46,57),
                   var2 = c(10.5,11,2,9,4,6,8,5.3,2.9,10))
```

```{r question_7, exercise=TRUE,exercise.lines = 12}
descript_stats <- summarise(data,
                           mean_var1 = ,
                            sd_var1 = ,
                            mean_var2 = ,
                            sd_var2 =
                            )

#Note: the summarise() function above has been separated onto multiple lines to help with legiability.

```

```{r question_7-hint-1}
If you're unsure of how to use the `summarise()` function, type help(summarise) into the console, or use Google.
```

```{r question_7-hint-2}
Arguments in a function are separated by commas.

Next hint will show the solution...
```

```{r question_7-solution}
descript_stats <- summarise(data,
                            mean_var1 = mean(var1),
                            sd_var1 = sd(var1),
                            mean_var2 = mean(var2),
                            sd_var2 = sd(var2)
                            )
```

```{r question_7-check}
checker()
```

### Question 8

Below is a data.frame called `data`. Use the `summarise()` function to calculate the maximum and minimum values from `var1` and `var2`. Save the resulting data.frame as `data_minmax` and name the new variables computed by the `summarise()` function in the following order: max_var1, min_var1, max_var2, and min_var2.

```{r, echo = FALSE}
data <- data.frame(ID = c(1,2,3,4,5,6,7,8,9,10),
                   var1 = c(10,92,NA,74,65,31,42,53,64,75),
                   var2 = c(10.5,11,2,9,4,6,8,5.3,2.9,10))
```
```{r}
data
```

```{r question_8-setup, include = FALSE}
data <- data.frame(ID = c(1,2,3,4,5,6,7,8,9,10),
                   var1 = c(10,92,NA,74,65,31,42,53,64,75),
                   var2 = c(10.5,11,2,9,4,6,8,5.3,2.9,10))
```

```{r question_8, exercise=TRUE,exercise.lines = 12}
data_minmax <-

```

```{r question_8-hint-1}
Remember to deal with missing data if necessary.
```

```{r question_8-hint-2}
Check that there are no typos in the new variable names. Also check that the new variables are in the order as specified above (this just helps check that you have the correct answer).

Next hint will show the solution...
```

```{r question_8-solution}
data_minmax <- summarise(data,
                          max_var1 = max(var1,na.rm = TRUE),
                          min_var1 = min(var1,na.rm = TRUE),
                          max_var2 = max(var2,na.rm = TRUE),
                          min_var2 = min(var2,na.rm = TRUE)
                          )
```

```{r question_8-check}
checker()
```

### Question 9

Below, we are attempting to make a numeric vector with three missing values. However, when we run `is.na(missing_values)`, R is telling us there are 0 missing values. Fix the code below so that `is.na(missing_values)` gives us the correct answer of three `FALSE` followed by three `TRUE`.

```{r question_9, exercise=TRUE,exercise.lines = 12}
missing_values <- c(4, 5, 6, "NA","NA","NA")

is.na(missing_values)

```

```{r question_9-hint-1}
Try running the code `class(missing_values)`. Does something seem wrong here?
```

```{r question_9-hint-2}
R differentiates character strings and object names from the use of quotation marks...

Next hint will show the solution...
```

```{r question_9-solution}
missing_values <- c(4, 5, 6, NA,NA,NA)

#quotation marks are removed around NA values.

is.na(missing_values)
```

```{r question_9-check}
checker()
```

### Question 10

Below is a character vector named `animals`. Determine how many missing values are in `animals` by using the functions `is.na()` and `sum()` and save the result as `NA_total`.

```{r question_10-setup, include = FALSE}
animals <- c("cat","magpie","lion","eagle","tiger",NA,"crow",NA,NA,"bulldog","hawk","kangaroo",NA,"swan",NA,NA,NA,NA)
```

```{r question_10, exercise=TRUE,exercise.lines = 12}
animals

NA_total <-

```

```{r question_10-hint-1}
`is.na()` returns a logical vector. Logical vectors are a special type of Factor class that at times can be treated as numeric, with FALSE = 0 and TRUE = 1.
```

```{r question_10-hint-2}
Check that there are no typos in the new variable names. Also check that the new variables are in the order as specified above (this just helps check that you have the correct answer).

Next hint will show the solution...
```

```{r question_10-solution}
animals

temp <- is.na(animals)
NA_total <- sum(temp)

#The above can be represented in one line of code:

NA_total <- sum(is.na(animals))
```

```{r question_10-check}
checker()
```

## Advanced Exercises

Sometimes, you will want to analyse data, but the variables of interest are in separate data.frames - maybe the data are from different sources, or collected using different programs. This week's advanced exercises focuses on merging two separate data.frames in R.

NOTE: Content in these advanced exercises are NOT covered in demonstrations. The purpose is to provide additional challenges or new R content for students looking for a challenge. Also, there is no code checking for advanced exercises - you are required to evaluate whether the code meets the objective on your own. However, if you want an example of a possible answer, you can click through the hints.

### Question A1 - Joining Data.frames

The R package `tidyverse` provides some handy functions for joining data.frames. Join functions are most useful in situations where different variables from the same participants are stored in separate data.frames. Here are some of the more useful join functions:

Function name|
-------------|------------------------------------------------------------------------
left_join()  |Keeps all the data in the first table, and adds columns from the second to rows that match.
right_join() |Keeps all the data in the second table, and adds columns from the first to rows that match.
inner_join() |Only returns rows that have a match in both tables.
full_join()  |Retains all information from both tables. If a row does not have a match in one table, it will receive a NA value for the other table's columns.

Each of the above functions joins two data.frames together. How they differ is what rows the function decides to retain/exclude. All of the above join functions have the same syntax:

```{r,echo = TRUE,eval = FALSE}
XXX_join(x, y, by = NULL, suffix = c(".x",".y"))
```

Let's break down each or the arguments

Argument|Description
--------|--------------------------------------------------------------
x       |The first table you want to join, known as the "left" table.
y       |The second table you want to join, known as the "right" table.
by      |The columns (variable names) you wish to join the two tables on (i.e., the variable you are 'matching' on). There must be a variable with this name in both tables.
suffix  |If columns have the same name in the two tables, you can add a suffix so you can distinguish between the two. The default for this is ".x" for the left table, and ".y" for the right table.

In this and the following questions, we will give examples of how these join functions work.

In the code below, we use a `full_join()` function to join the two data.frames `data.left` and `data.right`. Edit this code so that the columns "match" on the participant ID column. (Note: If you do not specify any columns to join on, these functions are smart enough to determine the best variable to match on, but it best to get in the habit of always specifying a column using the 'by' argument)

```{r question_a1-setup, include = FALSE}
data.left <- data.frame(participant_id = c(1:6),age = c(24,25,24,31,19,18),country_of_birth = c("Scotland","Scotland","England","Ireland","Scotland","England"),stringsAsFactors = FALSE)

data.right <- data.frame(participant_id = c(1:6),creativity = c(4,2,5,3,4,6),logical_reasoning = c(5,2,6,5,5,4),stringsAsFactors = FALSE)      
```

```{r question_a1, exercise=TRUE,exercise.lines = 8}
#data.left
#data.right

joined.data <- full_join(data.left,data.right,by = )

joined.data
```

```{r question_a1-hint-1}
Check the column names for each of the data.frames to see what variable distinguishes participants.
```

```{r question_a1-hint-2}
Make sure you specify the column within quotations (e.g., by = "variable_name").

Next hint will show the solution...
```

```{r question_a1-solution}
joined.data <- full_join(data.left,data.right,by = "participant_id")
```

### Question A2 - left_join()

`left_join()` is one of the more useful join functions. This function keeps all data from the first (left) table and joins all columns that has a matching row in the second (right) table. This is particularly helpful if there are cases (rows) in the right table that are not in the left (and is therefore not of interest to us), or if columns in the right table apply to multiple rows in the left table. By carefully considering which data.frame is on the left vs. right, in almost all cases, `left_join()` or `full_join()` will suit your needs.

In the box below, there are two data.frames. The `data.left` table from Question A1, and a new data.frame with country-level statistics called `data.countries`. Use `left_join()` to join these data.frames.

```{r question_a2-setup, include = FALSE}
data.left <- data.frame(participant_id = c(1:6),age = c(24,25,24,31,19,18),country_of_birth = c("Scotland","Scotland","England","Northern Ireland","Scotland","England"),stringsAsFactors = FALSE)

data.countries <- data.frame(country_of_birth = c("England","Northern Ireland","Scotland","Wales"),number_of_murders = c(484,24,59,242),stringsAsFactors = FALSE)      
```

```{r question_a2, exercise=TRUE,exercise.lines = 8}
#data.left
#data.countries

joined.data <- left_join(x, y, by = )

joined.data
```

```{r question_a2-hint-1}
Check the column names for each of the data.frames to see what variable distinguishes participants.
```

```{r question_a2-hint-2}
We are interested in keeping all data for our participants, so this data.frame should be on the left.

Next hint will show the solution...
```

```{r question_a2-solution}
joined.data <- left_join(data.left,data.countries,by = "country_of_birth")
```

Notice when using `left_join()`, there are no matches for "Wales" in the left data.frame, so this information is removed when using `left_join()`. Also, there are multiple matches for one country (e.g., Scotland); this function will join on both matched rows appropriately. Re-run the code above, but instead use `full_join()`, and compare the results to when you use `left_join()`.

### Question A3 - Matching on Multiple Variables

What if you need the join function to match on more than one variable? Thankfully, the join functions can accomodate this. Using the 'by' argument, rather than specifying one column, you can specify any number by putting the column names in a character vector. Remember, both data.frames need to have all match variables.

Below is data collected from three participants, who were tested in two countries. Currently, the data is in two separate data.frames. Use `left_join()` to merge the two data.frames correctly.

```{r question_a3-setup, include = FALSE}
data.1 <- data.frame(participant_id = c(1,2,3,1,2,3),age = c(24,25,24,31,19,18),country_of_birth = c("Scotland","Scotland","Scotland","Northern Ireland","Northern Ireland","Northern Ireland"),stringsAsFactors = FALSE)

data.2 <- data.frame(participant_id = c(1,2,3,1,2,3),country_of_birth = c("Scotland","Scotland","Scotland","Northern Ireland","Northern Ireland","Northern Ireland"),friendliness = c(1,7,6,4,5,3),stringsAsFactors = FALSE)  
```

```{r question_a3, exercise=TRUE,exercise.lines = 8}
#data.1
#data.2

joined.data <- 

joined.data
```

```{r question_a3-hint-1}
To create a vector, use the `c()` function. 
E.g., to create a character vector, you could use the code: `c("a","b")`
```

```{r question_a3-hint-2}
Make sure to specify all columns you wish to match on. If you need to check column names, call the data.frames.

Next hint will show the solution...
```

```{r question_a3-solution}
joined.data <- left_join(data.1,data.2,by = c("participant_id","country_of_birth"))
```

### Question A4 - Suffixes

How about a situation where both data.frames have variables with the same name, but you aren't joining on these variables. By taking advantage of the 'suffix' argument in the join functions, you can create a way to unambiguously distinguish between the variables from the different data.frames. This argument accepts a character vector with a length of two. The first element of the vector will be pasted on the end of the variables from the left data.frame, while the second element will be pasted on the end of the variables on the right data.frame.

A common situation where this could occur is data collected from the same participant at two different time points. In the box below, there are two data.frames collected from 6 participants, each data.frame representing data collected at a separate time point. Edit the code below to correctly join the data.frames.

```{r question_a4-setup, include = FALSE}
data.time1 <- data.frame(participant_id = c(1:6),age = c(24,25,24,31,19,18),satisfaction = c(4,3,4,5,4,5),stringsAsFactors = FALSE)

data.time2 <- data.frame(participant_id = c(1:6),age = c(26,27,26,33,21,20),satisfaction = c(6,6,5,5,2,7),stringsAsFactors = FALSE)
```

```{r question_a4, exercise=TRUE,exercise.lines = 8}
#data.time1
#data.time2

joined.data <- XXX_join(x, y, by = ,suffix = c(".time1",".time2"))

joined.data
```

```{r question_a4-hint-1}
Check the column names for each of the data.frames to see what variable distinguishes participants.
```

```{r question_a4-hint-2}
We are interested in keeping all data for our participants, so this data.frame should be on the left.

Next hint will show the solution...
```

```{r question_a4-solution}
joined.data <- left_join(data.time1, data.time2, by = "participant_id",suffix = c(".time1",".time2"))
```

To see what the suffix argument does, call the `joined.data` data.frame.

### Question A5 - bind_rows()

Up to now, we have exclusively dealt with join functions, which adds variables from one data.frame to another. A totally different way of merging data.frames together is combining rows. This is common when you have two data.frames with the same variables but different rows, e.g. data collected from different participants on the same task. This can be achieved by using the `bind_rows()` function. This function simply accepts two arguments: the two data.frames you wish to join.

In the example below, we have two data.frames that were taken from two different computers running the same experiment. We wish to combine the data.frames by adding the rows of one data.frame to another so that we can analyse the data altogether.

```{r,echo = TRUE,eval = FALSE}
complete.data <- bind_rows(data_computer1,data_computer2)
```

A couple of things to note. First, between the data.frames, the number of columns must be the same and they must have the same names (though they don't necessarily have to be in the same order). Second, if a row is duplicated between the two tables, the row will also be duplicated in the resulting table.

In the box below, use the `bind_row()` function to join the two data.frames about planets.

```{r question_a5-setup, include = FALSE}
planets_within_belt <- data.frame(planet = c("Mercury","Venus","Earth","Mars"),
                                  diameter_km = c(4878,12104,12756,6794),
                                  orbit_days = c(88,224,365.25,687),
                                  average.temp_c = c(427,480,14,-63),
                                  moons = c(0,0,1,2),stringsAsFactors = FALSE)

planets_beyond_belt <- data.frame(planet = c("Jupiter","Saturn","Uranus","Neptune"),
                                  diameter_km = c(142984,120536,51118,49532),
                                  orbit_days = c(11.86*365,29*365,84*365,1164.8*365),
                                  average.temp_c = c(-130,-130,-200,-200),
                                  moons = c(79,62,27,14),stringsAsFactors = FALSE)     
```

```{r question_a5, exercise=TRUE,exercise.lines = 8}
#planets_within_belt
#planets_beyond_belt

all_planets <-

all_planets
```

```{r question_a5-hint-1}
Use the `bind_rows()` functions. Make sure to include both data.frames as arguments.
```

```{r question_a5-hint-2}
Why not call the merged data.frame and learn some planet facts?

Next hint will show the solution...
```

```{r question_a5-solution}
all_planets <- bind_rows(planets_within_belt,planets_beyond_belt)
```
